\documentclass[10pt,letterpaper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{url}
\author{Spenser Gilliland\\
\url{Spenser309@gmail.com}\\
ID:A20254941}
\title{Final Project: Quantitative Evaluation of RTL Power Reduction Techniques}

\begin{document}

\maketitle
\bigskip

\begin{abstract}
Power reduction of integrated circuits is increasingly important due to current heat dissipation and battery capacity limits.  This project utilizes a number of techniques to reduce the power consumption of a pipelined adder.  Specifically, glitch reduction, operand isolation, enhanced clock gating and precomputation logic are utilized. The adder is a custom design already implemented in verilog available on the web from \cite{code}.
\end{abstract}

\pagebreak

\section{INTRODUCTION}


\section{IMPLEMENTATION}

Table \ref{tab:stages} shows the various implemenatation stages for this project. Each stage was evaluated based on timing slack, power, and area.

\begin{center}
\begin{tabular}{|c|c|}
\hline Stages & Description \\
\hline 
\hline Stage 0 & Benchmarks of the original circuit. \\ 
\hline Stage 1 & Benchmarks after enhanced clock gating \\ 
\hline Stage 2 & Benchmarks after glitch reduction \\ 
\hline Stage 3 & Benchmarks after operand isolation \\ 
\hline Stage 4 & Benchmarks after precomputation logic \\ 
\hline Stage 5 & Benchmarks utilizing all beneficial techniques \\ 
\hline 
\end{tabular} 
\end{center}

\section{RESULTS}

\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline Metrics & Clock Gating & Enhanced Clock Gating & Precomputation Logic\\
\hline 
\hline Total Power & & & \\
\hline Maximum Frequenc & & & \\
\hline Total Area & & & \\
\hline 
\end{tabular}
\end{center}


The testbench will be an exhaustive test bench of all reasonable combinations of the circuit.  In all possible pipeline stages.  This will be an enhancement to the current test bench.

\section{CONCLUSION}


\begin{thebibliography}{9}

\bibitem{requirements} ECE 530 High Performance VLSI/IC Systems Term Project (Fall 2011)
\bibitem{code} \url{https://github.com/Spenser309/fully_pipelined_adder/}

\end{thebibliography}

\end{document}
